Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2017-11-21 paper.tex
Update on Overleaf.

\documentclass{llncs}
%\usepackage{llncsdoc}
\usepackage{epsfig}
\usepackage{graphicx}

%\usepackage{caption}
%\usepackage{subcaption}

@@

\usepackage{url}
\usepackage{hyperref}

\pagestyle{empty}

@@

% ====================================================================
% Previous title versions
\iffalse

% Peter 31 Oct: Current title does not really reflect the topic I think:
%\title{Exploring approaches to probabilistic record linkage using similarity searching}
% Peter 31 Oct: What about
\title{Efficient and Effective Metric Space Indexing for Complete Record Linkage}

\title{Using Metric Space Indexing for Efficient Complete Record Linkage}

@@

% ====================================================================
%  Hidden For Blind Review
\iffalse

\author{{\"O}zg{\"u}r Akg{\"u}n\inst{1} \and Alan Dearle\inst{1} \and Graham Kirby\inst{1}
\and Peter Christen\inst{2}}

\institute{School of Computer Science, University of St Andrews, St Andrews, Scotland.\\
Contact: \email{ozgur.akgun@st-andrews.ac.uk}
\and
Research School of Computer Science, The Australian National University, Canberra, Australia.\\
Contact: \email{peter.christen@anu.edu.au}}

@@

\begin{abstract}
%Probabilistic
Record linkage is the process of identifying records that refer to the
same real-world entities, in situations where entity identifiers are
unavailable. Records are linked on the basis of similarity between
common attributes, with every pair of records being classified as a
link or non-link depending on the degree of similarity between them.
Record linkage is usually performed in a three-step process, where first
groups of similar candidate records are identified using indexing. Only
pairs within the same group are then compared in more detail, and
finally classified.
%
Even state-of-the-art indexing techniques, such as Locality Sensitive
Hashing, have potential drawbacks. They may fail to group together some
true matching records with high similarity. Conversely, they may group
records with low similarity, leading to high computational overhead.
%
We propose using metric space indexing to perform \emph{complete} record
linkage, which results in a parameterless record linkage process
combining indexing, comparison and classification into a single step
delivering high effectiveness and efficiency.

@@

% 1 1/2 pages maximum!

@@

% Peter, 20171112:

Record linkage, also known as entity resolution, data matching and
duplicate detection~\cite{Chr12}, is the process of identifying and
matching records that refer to the same real-world entities within or
across datasets. The entities to be linked are often people (such as
patients in hospital or customers in business datasets), but record
linkage can also be applied to link consumer products or bibliographic
records~\cite{Chr12}. Record linkage is commonly challenged by the lack
of unique entity identifiers (keys) in the datasets to be linked, which
prevents the use of a database join. Instead, the linkage of records
requires the comparison of the common attributes (or fields) that are available
in the datasets to be linked. For datasets that contain
information about individuals, these attributes include the names,
address, dates of birth, and so on, of individuals.

@@

\begin{figure}[!t]
  \centering
  %\scalebox{1.0}[1.0]
  \includegraphics[width=1.0\textwidth]{figures/linkage-process}
  \caption{Overview of the steps of the traditional record linkage
           process (left-hand side) and our proposed metric space
           indexing based approach (right-hand side), as described in
           Sect.~\ref{sec-intro}, where records from two datasets,
           $\mathbf{D}_A$ and $\mathbf{D}_B$, are being linked.}
           \label{fig-rl-process}
\end{figure}

@@

% Repeat:
% If a certain blocking approach results in a loss of recall in the
% final linkage results, as determined by post auditing, the blocking
% needs to be redone, an often time consuming process.

Here we explore how existing indexing techniques can lead to
reduced recall, even for record pairs that are highly similar and likely
correspond to true matches. As a result, such techniques can lead
to \emph{incomplete} record linkage results. To address this problem,
\emph{metric space indexing} (MSI) can be used to guarantee that all
record pairs, up to a certain distance threshold, are considered in the
record linkage results. MSI also avoids the need for costly detailed
comparison of record pairs with low similarities, which may be inserted
into the same block with traditional indexing techniques. It allows
indexing, comparison and classification to be combined into a
single step, as shown in Fig.~\ref{fig-rl-process}, making the overall
record linkage process simpler, more efficient and more effective than
the traditional approach.

% Sanity check this claim in final version.

% Peter 20171112: do we also need to mention we do not waste
% comparisons of record pairs with low similarities (i.e. those with
% a distance > max_dist)?

%to add: something about similarity spaces / metric spaces, M-trees and its more recent advanced/improved versions, and how they have been used in similarity search.}
%to add: How our work is different from these other metric space works, and description of our contributions.

\smallskip
%Al - I have beefed this up and added a fourth contribution.
\textbf{Contributions:} We make four specific contributions: (1) We
investigate how existing indexing techniques can result in
\emph{incomplete} record linkage results. (2) We show that these
techniques are highly sensitive to parameter settings and can produce
very low quality linkage. (3) We explore MSI for record linkage and
propose an approach that achieves consistently \emph{complete},
efficient and effective record linkage. (4) We evaluate our approach on
several data sets from diverse domains and show its advantages over
existing indexing techniques for record linkage.

% *******************************************************
% we can't write this as it reveals us in the double-blind review
% we can add to final paper:
% The motivation for this work is the Digitising Scotland project (Dibben 2012), which is in the process of transcribing and linking all the vital events recorded in Scotland between 1856 and 1977. This data set will, when complete, include around 14 million birth records, 11 million death records and 4 million marriage records. As part of the work, certain data fields (locations, occupations and causes of death) are also being classified to the relevant standard coding schemes.
% *********************************************************

@@

Locality sensitive hashing (LSH), originally proposed to allow
efficient nearest-neighbor search in high-dimensional
spaces~\cite{Ind98}, has been employed in record linkage as an indexing
technique where attribute values are hashed multiple times, and
blocks are created from those records that share some hash values.
\emph{HARRA}~\cite{Kim10} is a record linkage approach based on Min-hash
[CITATION?] and LSH
which blocks, compares, and then merges linked records in an iterative
fashion, where merged records are re-hashed to improve overall linkage
quality. Steorts et al.~\cite{Steorts2014} recently evaluated two LSH
variations, with their main conclusion being that in order to get good
results LSH methods must be tuned to the particular datasets being
linked. This requires good quality ground truth data which may be
unavailable or very expensive to obtain.

@@

% Do we need to spell out that the inter-node distances are the
% distances between the corresponding indexed records?

@@

\cite{Li2006} describes a threshold-based method of performing linkage
using R-trees~\cite{Hjaltason1998}. It demonstrates that high quality
may be achieved using Jaccard similarity over selected record fields.
% Is next sentence necessary?
The approach achieved a recall of 99 percent in experiments in which
conjunctions of similarities over fields were used.
% Is this execution-time efficiency?
A later paper \cite{Ciaccia97indexingmetric} shows that M-trees are
almost always more efficient than R-trees, hence their use in the
experiments described in this paper.

% end of related work should be around end of page 3!

@@

The general problem we address is that for two datasets A and B, we wish
to find all the records from dataset B that match each record from dataset A.
We explore the efficacy of several similarity search algorithms for
record linkage: traditional blocking, one popular incomplete algorithm, LSH-minhash, and one complete
method, M-tree~\cite{paolociaccia2m}. We also use a simple brute force
(nested-loop) exact technique as a baseline for comparison, although
this approach can only feasibly be applied to the smallest of our
datasets. All experiments have a number of parameters with which we can
configure the search space and algorithm behaviour, as described in
Sect.~\ref{sec-exp}. A \emph{distance threshold}, $d$, specifies a
maximum distance, equivalent to a minimum similarity, for two records to
be classified as a link (i.e.\ referring to the same entity).

\smallskip
\textbf{Nested loop:}
In the brute force approach two nested loops are used to compare every 
record with every other record. The complexity of this 
approach is quadratic in the number of records to
be linked. This approach is guaranteed to identify all links, i.e. record pairs within the given distance threshold, $d$.

\smallskip
\textbf{Traditional  blocking:}
In the traditional blocking technique records are blocked using hand selected keys as described in \cite{Chr12b}. The keys are chosen with the intention of giving the best possible results for the dataset. Multiple blocking keys are commonly used to address the problem of missing and erroneous values preventing matches from being found. Often the choice of blocking keys requires intimate knowledge of the domain and of the records being linked.

\smallskip
\textbf{LSH-MinHash:}
The LSH-minhash algorithm used has three tuning parameters:
\emph{shingle size}, $l_{ss}$, the \emph{band size}, $l_{bs}$, and the
\emph{number of bands}, $l_{nb}$.
These are explained in the following algorithm description which follows a standard LSH approach \cite{Ind98}.
Using this approach, each record drawn from a set of records is placed in a \emph{LSH-MinHash} data structure.
To do this, for each record, firstly all the fields of the record are turned into strings and 
concatenated. Next the strings are \emph{shingled} into a set of
n-grams (sub-strings of length $n$) according to the $l_{ss}$
parameter (i.e.\ $n = l_{ss}$). Next a set of randomly, 
deterministically generated hash functions are applied to each of the
sets of n-grams and the smallest (the minhash) of each application is
added to a signature. The number of hashes used and thus the size of
the signature is set to $l_{nb} \times l_{bs}$.
Lastly the signature is divided into $l_{nb}$ bands and the values  from each band are hashed again to create a number of keys.
The original record is added to a map associated with each of the keys.

To perform linkage the following procedure is followed: for each query, the value is hashed using the procedure described above and the union of the set of values found for all hashes in the map are returned. These are then filtered by performing distance calculations on the results to eliminate false positives.

\smallskip 
\textbf{M-Tree:} The M-tree experiments have no parameters. In a similar manner to the \emph{LSH-MinHash} approach, M-trees are constructed by supplying the implementation with a set of records and a \emph{distance function}. The distance functions used are the same as those used for \emph{Nested-loop} and \emph{LSH-MinHash} experiments. To perform linkage the data-structure is searched using a \emph{range-search} query which yield all records within distance $d$ of the query object and all the returned records are directly recorded as links.

@@

We now describe the data sets we use in our evaluation, the setup
employed to evaluate our proposed metric indexing approach and
compare it with traditional blocking techniques, and we then present
and discuss our results.

@@

\smallskip
\textbf{Data Sets:}
%\label{sec-data}
We used four real data sets from three domains in our experiments as
summarized in Table~\ref{table-datasets}. The first is
\emph{CORA}~\footnote{Available from:
\texttt{http://secondstring.sourceforge.net}}, which contains 1,295
records that refer to 112 machine learning publications. Ground truth is provided via a unique
\emph{paper\_id} identifier of the form "blum1993". In this experiment linkage is performed over the same set of records.

The second are two randomly selected sub-sets extracted from the North Carolina Voter Registration
database (\emph{NCVR})~\footnote{Available from: \texttt{http://dl.ncsbe.gov/}}, which were collected in April and June
2014. Each of these contains records of voters and includes their
first names, surnames, and addresses. Ground truth is provided via a
\emph{NCID} identifier which uniquely identifies a voter.

The last two data sets are historical Scottish records of vital
events (birth, marriages and deaths) registered on the
\emph{Isle of Skye}, a rural district, while the other contains
records from \emph{Kilmarnock}, an industrial town. These data sets
were provided to us by the demographer and historians who extensively
curated and linked both data sets~\cite{reid2002,reid2006}. Both data
sets include the  names, gender, addresses of individuals and their
parents. Ground truth was generated by the demographers based on their
extensive domain knowledge.

@@

\smallskip
\textbf{Experimental Setup:}
%
We implemented all techniques described in Sect.~\ref{sec-approach}
using Java (version 1.8.0\_144) and ran an extensive set of experiments on
a compute server with 24 Intel(R) Xeon(R) processors running at 2.30GHz, 
128 GBytes of main memory and running Red Hat 4.8.5-11.

The parameter settings used in our experiments are summarized in
Table~\ref{table-parameters}. ... \emph{describe and justify selected
values..}

@@

Do BruteForce, LSH and M-Tree

1.1 BruteForce

%the following is a sentence we culled earlier but may be needed.
We we will evaluate the performance of LSH based blocking with regard to the three parameters $l_{ss}$, $l_{bs}$ and $l_{nb}$ in
Sect.~\ref{sec-exp}.

\smallskip
\textbf{Results and Discussion}

%\subsection{Results and Discussion}
%\label{sec-results}

table or plots?

@@

\section{Conclusions and Future Work}
\label{sec-concl}

@@

\bibliographystyle{splncs03}
%\bibliographystyle{abbrv}
\bibliography{paper.bib}

@@

\if

>>>>

\documentclass{llncs}
\usepackage{epsfig}
\usepackage{graphicx}

@@

\usepackage{url}
\usepackage{hyperref}
\usepackage{cleveref}

%\pagestyle{empty}
\pagestyle{headings}

@@

\title{Using Metric Space Indexing for Complete and Efficient Record Linkage}

@@

%  Hidden For Blind Review
\iffalse

\author{{\"O}zg{\"u}r Akg{\"u}n\inst{1} \and Alan Dearle\inst{1} \and\\
Graham Kirby\inst{1} \and Peter Christen\inst{2}}

\institute{School of Computer Science, University of St Andrews,\\
St Andrews, Scotland. Contact: \email{ozgur.akgun@st-andrews.ac.uk}
\and
Research School of Computer Science, The Australian National University,\\
Canberra, Australia. Contact: \email{peter.christen@anu.edu.au}}

@@

\begin{abstract}

Record linkage is the process of identifying records that refer to the
same real-world entities, in situations where entity identifiers are
unavailable. Records are linked on the basis of similarity between
common attributes, with every pair of records being classified as a
link or non-link depending on the degree of similarity between them.
Record linkage is usually performed in a three-step process: first
groups of similar candidate records are identified using indexing; 
pairs within the same group are then compared in more detail, and
finally classified.
%
Even state-of-the-art indexing techniques, such as Locality Sensitive
Hashing, have potential drawbacks. They may fail to group together some
true matching records with high similarity. Conversely, they may group
records with low similarity, leading to high computational overhead.
%
We propose using metric space indexing to perform \emph{complete} record
linkage, which results in a parameterless record linkage process
combining indexing, comparison and classification into a single step
delivering complete and efficient record linkage.

@@

@@

Record linkage, also known as entity resolution, data matching and
duplicate detection~\cite{Chr12}, is the process of identifying and
matching records that refer to the same real-world entities within or
across datasets. The entities to be linked are often people (such as
patients in hospital or customers in business datasets), but record
linkage can also be applied to link consumer products or bibliographic
records~\cite{Chr12}. Record linkage is commonly challenged by the lack
of unique entity identifiers (keys) in the datasets to be linked, which
prevents the use of a database join. Instead, the linkage of records
requires the comparison of the common attributes (or fields) that are
available within the datasets. For datasets that contain information
about individuals, these attributes include the names, address, dates of
birth, and so on, of individuals.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=1.0\textwidth]{figures/linkage-process}
  \caption{Overview of the steps of the traditional record linkage
           process (left-hand side) and our proposed metric space
           indexing based approach (right-hand side), as described in
           Sect.~\ref{sec-intro}, where records from two datasets,
           $\mathbf{D}_A$ and $\mathbf{D}_B$, are being linked.}
           \label{fig-rl-process}
\end{figure}

@@

\textbf{TODO: GK rewrite this paragraph. Make the connection between completeness and high recall. Define completenes.}
Here we explore how existing indexing techniques can lead to
low recall, even for record pairs that are highly similar and likely
correspond to true matches. As a result, such techniques can lead
to \emph{incomplete} record linkage results. To address this problem,
\emph{metric space indexing} (MSI) can be used to guarantee that all
record pairs, up to a certain distance threshold, are considered in the
record linkage results. MSI also avoids the need for costly detailed
comparison of record pairs with low similarities, which may be inserted
into the same block with traditional indexing techniques. It allows
indexing, comparison and classification to be combined into a
single step, as shown in Fig.~\ref{fig-rl-process}, making the overall
record linkage process simpler, more efficient and more effective than
the traditional approach.

\textbf{Contribution:} The primary contribution of this paper is the novel application of MSI to achieve complete and efficient record linkage, without the need for complex parameter tuning.
We evaluate our approach on several data sets from diverse domains and demonstrate its advantages over
existing indexing techniques for record linkage.

% For final paper:
% The motivation for this work is the Digitising Scotland project (Dibben 2012), which is in the process of transcribing and linking all the vital events recorded in Scotland between 1856 and 1977. This data set will, when complete, include around 14 million birth records, 11 million death records and 4 million marriage records. As part of the work, certain data fields (locations, occupations and causes of death) are also being classified to the relevant standard coding schemes.

@@

Locality sensitive hashing (LSH), originally proposed to allow efficient
nearest-neighbor search in high-dimensional spaces~\cite{Ind98}, has
been employed in record linkage as an indexing technique where attribute
values are hashed multiple times, and blocks are created from those
records that share some hash values. \emph{HARRA}~\cite{Kim10} is a
record linkage approach based on MinHash~\cite{Broder1997} and LSH which
blocks, compares, and then merges linked records in an iterative
fashion, where merged records are re-hashed to improve overall linkage
quality. ~\cite{Steorts2014} evaluates two LSH variations, concluding
that in order to get good results, LSH methods must be tuned to the
particular datasets being linked. This requires good quality ground
truth data which may be unavailable or expensive to obtain.

@@

@@

\cite{Li2006} describes a threshold-based linkage method
using R-trees~\cite{Hjaltason1998}. It demonstrates that high quality
may be achieved using Jaccard similarity over selected record fields.
\cite{Ciaccia97indexingmetric} shows that M-trees are
almost always more efficient than R-trees, hence their use in the
experiments described in this paper.

@@

We address the following general record linkage problem: for two
datasets $A$ and $B$, we wish to find, for each record in $A$, all the
records in $B$ that match it. We compare several algorithms for record
linkage: traditional blocking, one incomplete similarity search method,
LSH-MinHash, and one complete method, M-tree~\cite{paolociaccia2m}. We
also use a simple brute-force complete technique as a baseline for
comparison, although this can only feasibly be applied to the smallest
of our datasets. All experiments have a number of parameters to
configure the search space and algorithm behaviour, including a
\emph{distance threshold} specifying a maximum distance, equivalent to a
minimum similarity, for two records to be classified as a link (i.e.\
referring to the same entity).

\textbf{Brute-force:}
Two nested loops are used to compare every record in $A$ with every
record in $B$. Each pair is classified as a link if the distance between
the records is less than the threshold. This approach is guaranteed to
identify all links, with complexity $ O(|A| \times |B|) $.

\textbf{Traditional  blocking:}
The additional parameters are the set of blocking keys and the
normalization encodings applied to each field. These are selected as
described in \cite{Chr12b}, exploiting knowledge of the domain and of
the records being linked, and chosen with the intention of giving the
best possible results for the datasets.
%
Each record in $A$ is placed into the appropriate block based on its
blocking key value. The algorithm then iterates over the records in $B$,
and for each one, compares it with each of the records from $A$ in the
block with the same blocking key value.

\textbf{LSH-MinHash:}
The additional parameters are \emph{shingle size} ($l_{ss}$), \emph{band
size} ($l_{bs}$) and \emph{number of bands} ($l_{nb}$). Each record in
$A$ is placed in an \emph{LSH-MinHash} data structure. First, all the
fields of the record are concatenated, and the result \emph{shingled}
into a set of n-grams with $n = l_{ss}$. Next, a set of 
deterministically generated hash functions are applied to
each n-gram in the set
and the smallest result (the MinHash) of each hash application is added
to a signature for the record. The number of hashes used, and thus the
size of the signature, is set to $l_{nb} \times l_{bs}$. Finally, the
signature is split into $l_{nb}$ bands and the values from each band
are hashed again to create a number of keys. The original record is
added to a map associated with each of the keys.

To perform linkage, the algorithm iterates over the records in $B$. Each
record is hashed using the procedure described above, to obtain a set of
keys. For each of these keys, the key is looked up in the LSH-MinHash
data structure, and the records from $A$ associated with it added to the
result set. Finally, the record from $B$ is compared in turn with each
record in the result set, with the pair being classified as a link or
non-link based on their distance.

\textbf{M-Tree:} The M-tree linkage algorithm has no additional parameters. In a similar manner to the \emph{LSH-MinHash} approach, M-trees are constructed by supplying the implementation with a set of records and a \emph{distance function}. The distance functions used are the same as those used for \emph{Nested-loop} and \emph{LSH-MinHash} experiments. To perform linkage, the data-structure is searched using a \emph{range-search} query which yields all records within distance $d$ of the query object and all the returned records are directly recorded as links.

@@

We now describe the data sets we use in our evaluation, the setup
employed to evaluate our proposed metric indexing approach and
compare it with traditional blocking techniques, and we then present
and discuss our results~\footnote{The raw data, additional figures and the source code required to run these experiments can be downloaded from here. (Link removed for double blind review)}.

@@

\smallskip
\textbf{Data Sets:}
%\label{sec-data}
We used four data sets from three domains in our experiments, as
summarized in Table~\ref{table-datasets}. The first is
\emph{CORA}~\footnote{Available from:
\texttt{http://secondstring.sourceforge.net}}, which contains 1,295
records that refer to 112 machine learning publications. 
It is used as a benchmark data set in the literature for assessing linkage algorithms. Ground truth is provided via a unique
\emph{paper\_id} identifier of the form "blum1993". In this experiment linkage is performed over the same set of records.

The second are two randomly selected sub-sets extracted from the North Carolina Voter Registration
database (\emph{NCVR})~\footnote{Available from: \texttt{http://dl.ncsbe.gov/}}, which were collected in April and June
2014. Each of these contains records of voters including their
first names, surnames, and addresses. Ground truth is provided via a
\emph{NCID} identifier which uniquely identifies a voter.

The last two data sets are historical Scottish records of vital
events (birth, marriages and deaths) one registered on the
\emph{Isle of Skye}, a rural district, and the other
records from \emph{Kilmarnock}, an industrial town. These data sets
were provided to us by historical demographers who extensively
curated and linked both data sets~\cite{reid2002,reid2006}. Both data
sets include the  names, gender, addresses of individuals and their
parents. Ground truth was generated by the demographers based on their
extensive domain knowledge.

@@

% \smallskip
% \textbf{Experimental Setup:}
% %
% We implemented all techniques described in Sect.~\ref{sec-approach}
% using Java (version 1.8.0\_144) and ran an extensive set of experiments on
% a compute server with 24 Intel(R) Xeon(R) processors running at 2.30GHz, 
% 128 GBytes of main memory and running Red Hat 4.8.5-11.

The parameter settings used in our experiments are summarized in
Table~\ref{table-parameters}.

In all of our experiments we use a single distance metric which is the sum of the Levenshtein distances between the set of fields being compared.

@@

In this section, we perform linkage on the Cora data set using all four approaches presented in this paper: brute force, traditional blocking, LSH and M-Tree.
The brute-force approach is used to establish the threshold value that yields the best possible linkage for the Cora dataset. The threshold value is varied between 0 and 250, \Cref{fig-cora-quality} presents the precision, recall, and F-measure values. 
The linkage results have high precision and low recall for low threshold values, and high recall and low precision for high threshold values.
For this data set, the maximum F-measure value is achieved using a threshold value of 70. This value is data dependent; for different datasets the maximum F-measure will correspond to different thresholds. 
In the rest of this section we fix the threshold value to be 70 which maximises the F-measure for this dataset.

\begin{figure}
\begin{verbatim}
Figure 3 will be a table of Comparisons, F1, precision recall and pairs stuff.
12 ROWS ISH
\end{verbatim}
\caption{Linkage Quality using Brute Force linking on the Cora data set\label{fig-cora-quality}}
\end{figure}

\subsubsection{Traditional Blocking}

Traditionally, blocking is a method for choosing candidates for linkage using manually designed criteria.
Thanks to blocking, a distance is only computed between promising pairs of records.
A major disadvantage of traditional blocking is the need for extra engineering effort.
Bespoke blocking strategies need to be designed for a given data set and application domain.
In this section we experiment with using each key field in the Cora data set as a blocking key one by one, followed by a very permissive blocking key which takes the union of all the blocks attained by using individual key fields.

\emph{AL: The above needs more explanation and not the first bit?}

TODO: Explain pairs-quality and pairs-completeness~\Cref{cora-traditional}.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotFixedThresholdTraditional2_--_Cora_-_TradBlocking_-_70}
\caption{Blocking Quality using traditional blocking on the Cora data set\label{cora-traditional}}
\end{figure}

\Cref{cora-traditional-prf} plots the linkage quality values obtained by running traditional blocking based linkage at a threshold level of 70. Here, we see that high precision values are possible using blocking based linkage, however the recall (and as a result the F-measure) is poor in comparison to brute-force.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotFixedThresholdTraditional1_--_Cora_-_TradBlocking_-_70}
\caption{Linkage Quality using traditional blocking on the Cora data set\label{cora-traditional-prf}}
\end{figure}

\subsection{LSH}

LSH is a method for performing blocking without the engineering overhead of traditional blocking.
It is parameterised over two integer values: number of bands, and band sizes~\footnote{LSH can also be parameterised over the shingle size, but in this paper we set the shingle size to 2.}.

\subsection{M-Tree}

M-Tree is a complete method that avoids brute-force search.
In addition, it does not require any additional engineering work, it works with any distance metric.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_Brute_Force}
\caption{Block Quality - Brute Force\label{cora-block-quality-brute}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_MTree}
\caption{Block Quality - M-Tree\label{cora-block-quality-mtree}}
\end{figure}

\subsection{Historical Demography results}
\begin{itemize}
\item Fig X -1 Repeat of figure 2 with precision recall comparisons etc.
\item Fig X - Kilmarnock M tree plot Precision,recall and F
\item Fig X + 1 - Skye M tree plot Precision,recall and F
\item Fig X + 2 - Mtree F measure and a bunch LSH F measures.
\end{itemize}

\subsection{NCVR}

@@

\section{Conclusions and Future Work}

\textbf{Contribution:} The primary contribution of this paper is the novel application of MSI to achieve complete and efficient record linkage, without the need for complex parameter tuning.
We evaluate our approach on several data sets from diverse domains and demonstrate its advantages over
existing indexing techniques for record linkage.

\label{sec-concl}

@@

\bibliographystyle{splncs03}
\bibliography{paper.bib}

@@

%the following is a sentence we culled earlier but may be needed.
We will evaluate the performance of LSH based blocking with regard to the three parameters $l_{ss}$, $l_{bs}$ and $l_{nb}$ in
Sect.~\ref{sec-exp}.

\begin{verbatim}
for each record a in A
    for each record b in B
        classify (a,b) as link if distance(a,b) < threshold
\end{verbatim}
